MSHS COVID-19 Vaccination Summary

### 2022-04-13 MSH Admin Dose Summary.Rmd
Update new vaccine summary dashboard and fix typos.

#Analysis for weekend discharge tracking
library(readxl)
library(writexl)
library(ggplot2)
library(lubridate)
library(dplyr)
library(reshape2)
library(svDialogs)
library(stringr)
library(formattable)
library(scales)
library(ggpubr)
library(reshape2)
library(knitr)
library(kableExtra)
library(rmarkdown)
library(zipcodeR)
library(tidyr)
library(purrr)
library(janitor)
```

@@

# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Weekly Dashboard Doses Administered",
  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-05.xlsx"))

@@

kable(subset_data,
      format = "html",
      escape = FALSE,
      align = "l",
      digits = 0,
      caption = paste("MSHS", setting, vax_type,
                      "Vaccine Doses Administered"))%>%
  kable_styling(bootstrap_options = "hover", 
                font_size = 11,
                full_width = FALSE) %>%
  row_spec(row = 0,
           background = "#221f72",
           color = "white") %>%
  row_spec(row = nrow(subset_data),
           bold = TRUE,
           italic = TRUE)

@@

### Hospital Based PODS
```{r Create tables for hospital POD vaccine summary}

@@

>>>>

#Analysis for weekend discharge tracking
library(readxl)
library(writexl)
library(ggplot2)
library(lubridate)
library(dplyr)
library(reshape2)
library(svDialogs)
library(stringr)
library(formattable)
library(scales)
library(ggpubr)
library(reshape2)
library(knitr)
library(kableExtra)
library(rmarkdown)
library(zipcodeR)
library(tidyr)
library(purrr)
library(janitor)
library(DT)
```

@@

# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Weekly Dashboard Doses Administered",
  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-11.xlsx"))

@@

kable(subset_data,
      format = "html",
      escape = FALSE,
      align = "l",
      digits = 0,
      caption = paste(setting, vax_type,
                      "Vaccine Doses Administered"))%>%
  kable_styling(bootstrap_options = "hover", 
                font_size = 11,
                full_width = FALSE) %>%
  row_spec(row = 0,
           background = "#221f72",
           color = "white") %>%
  row_spec(row = nrow(subset_data),
           bold = TRUE,
           italic = TRUE)

@@

### Hospital POD
```{r Create tables for hospital POD vaccine summary}

@@

### Reference

**Data Source**

Analysis based on Epic schedule data.

***

**Department Mappings**
```{r Reference tab with data sources and mappings}
dept_mappings_dt <- dept_mappings %>%
  # relocate(`Setting Grouper`) %>%
  relocate(Department, .after = `New Site`) %>%
  relocate(`Vaccine Age Group`, .after = Department) %>%
  rename(Site = `New Site`,
         Setting = `Setting Grouper`,
         `Vaccine Administered` = `Vaccine Age Group`) %>%
  mutate(Setting = ifelse(Setting %in% "School Based Practice",
                          "MSHS Practice", Setting),
         `Vaccine Administered` = ifelse(`Vaccine Administered` %in% "Both",
                                         "Adult & Peds",
                                         `Vaccine Administered`)) %>%
  arrange(Setting, Site, Department)

datatable(dept_mappings_dt,
          rownames = FALSE,
          options = list(
            pageLength = 20,
            paging = TRUE
          ))
